A ``Dream'' Interface Design

### 2014-11-25 dream-design/dream-design.tex
new wireframes

In this investigation, I propose a ``dream'' interface design for touchscreen mobile devices that focuses on providing as much as feedback as possible. This feedback is designed in a way that can be helpful for individuals with and without visual impairments alike. The design in its entirety was created with the usability metrics of learnability, efficiency, and error rate in mind.

My ``dream'' interface design incorporates functionality of a product that is currently being developed by Tactus Technology, a company in Fremont, California \cite{Tactus}. Tactus Technology creates real physical buttons that dynamically appear and disappear into a flat touch screen (see Figure~\ref{tactus}). Small fluid channels are routed throughout the Tactile Layer and enable fluid to expand the top polymer layer to create the physical buttons \cite{Tactus}.

Although this technology from Tactus is extremely bleeding-edge, the prototypes have already received a fair amount of recognition and awards \cite{CNN, I-Zone, PCMag, Wired}. Reviewers have articulated how the technology seems to be ``downright magical'' \cite{CNN}. Though the look and feel of Tatctus technology is totally futuristic, the technology is already beginning to appear in consumer devices. In 2013, Touch Revolution, the ``largest-volume glass projected capacitive multi-touch screen manufacturer in the world'', announced a partnership with Tactus Technology \cite{TactusAvailability}. The technologies are being combined and manufactured into consumer devices today. Companies will also be able to customize the panel for different types of buttons, say for example, the buttons on a TV remote. This ``dream'' user interface design makes use of the fact that the possibilities for the panel are varied.

\begin{figure}[ht]
\centering
\includegraphics[width=4.5in]{tactus1.jpg} 
\caption{Tactus Technology keyboard}
\label{tactus}
\end{figure}

\section{Top-Level Design}
The design of this ``dream'' interface aims to assist users with visual impairments and users without visual impairments alike. The design includes an optional physical grid, tactile buttons of varying sizes, and auditory feedback.

\subsection{Grid-like Tactile Support}
The design will use Tactus technology to create a physical grid-like layout on the screen. This layout IBSVI so that they can engage their spatial cognition, perception and sensing resources while interacting with touch screens. The design will only enable the grid-like system on-command so to not distract or annoy those who do not benefit from it.

\begin{figure}[ht]
\centering
\includegraphics[width=1in]{wireframe.png} 
\caption{Tactus Technology keyboard}
\label{tactus}
\end{figure}

The tactile stuff is intended to operate in conjunction with other technologies that provide auditory feedback that informs the users of \textit{what} is at the location on the screen while the tactile buttons heps the user know \textit{where} it is. 
\label{background}

@@

\section{Rationale}

>>>>

In this investigation, I propose a ``dream'' interface design for touchscreen mobile devices that focuses on providing the user with as much as feedback as possible. This feedback is designed in a way that aims to be helpful for users with visual impairments and users without visual impairments alike. The design in its entirety was created with the usability metrics of learnability, efficiency, and error rate in mind.

My ``dream'' interface design incorporates functionality of a product that is currently being developed by Tactus Technology \cite{Tactus}. Tactus Technology, a company based in Fremont, California, creates real physical buttons that dynamically appear and disappear into a flat touch screen (see Figure~\ref{tactus1}). Small fluid channels are routed throughout the Tactile Layer and enable fluid to expand the top polymer layer to create the physical buttons \cite{Tactus}.

Although this technology from Tactus is extremely bleeding-edge, the prototypes have already received a fair amount of recognition as well as several awards \cite{CNN, I-Zone, PCMag, Wired}. Reviewers have articulated how the technology seems to be ``downright magical'' \cite{CNN}. Though the look and feel of Tatctus technology seems totally futuristic, the technology is already beginning to appear in consumer devices. In 2013, Touch Revolution, the largest-volume glass projected capacitive multi-touch screen manufacturer in the world, announced a partnership with Tactus Technology \cite{TactusAvailability}. The technologies are being combined and manufactured into consumer devices today \cite{TactusAvailability}. Not only is this technology becoming more and more available, but it is becoming more customizable as well. Companies will soon be able to customize the panel for different types of buttons, say for example, the buttons on a TV remote \cite{CNN}.

\begin{figure}[ht]
\centering
\includegraphics[width=4.5in]{tactus2.jpg} 
\caption{Tactus Technology keyboard}
\label{tactus1}
\end{figure}

My ``dream'' user interface design makes use of the tactile feedback as well as the flexibility that this technology from Tactus provides.

\section{Top-Level Design}
The objective of this ``dream'' interface design is to make mobile touchscreen devices more usable for individuals with visual impairments and individuals without visual impairments alike. The three main features designed to accomplish this goal are the optional physical grid, the tactile buttons of varying sizes, and the auditory feedback.

\subsection{Optional Physical Grid}
The design incorporates Tactus technology to pa physical grid-like layout on the screen.

\begin{figure}[ht]
\centering
\includegraphics[width=1.5in]{wireframe-grid.png} 
\caption{Example Grid Layout}
\label{wireframe-grid}
\end{figure}

The tactile stuff is intended to operate in conjunction with other technologies that provide auditory feedback that informs the users of \textit{what} is at the location on the screen while the tactile buttons heps the user know \textit{where} it is.

\subsection{Tactile Buttons}

\subsection{Auditory Feedback}

@@

\section{Rationale}
The design incorporates Tactus technology to pa physical grid-like layout on the screen. This layout IBSVI so that they can engage their spatial cognition, perception and sensing resources while interacting with touch screens. The design will only enable the grid-like system on-command so to not distract or annoy those who do not benefit from it.
